Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-26 num_result.tex
[figure] update py scripts and replot.

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$. The total system size is $N=35k$ sites with the same parameters in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtle zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi, 0.24\pi$ and $0.48\pi$. The finite size effect do not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=1\columnwidth]{PP_fit.pdf}
    \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) $\text{P}+\text{P}\rightarrow\lambda+\text{P}$. The parameters are the same as those in Fig.~\ref{fig:DDNN}. The plot is symmetric with respect to $\theta=0.25\pi$ as predicted. The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.08\pi,0.18\pi$ and $0.24\pi$. The finite size effect do not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
    \label{fig:PPPP}
    \todo[inline]{Mao: Put the PP for echo;}
\end{figure}

>>>>

\begin{figure}
  \centering
\includegraphics[width=1\columnwidth]{DDNN_fit.pdf}
\includegraphics[width=1\columnwidth]{DDNN_fidel_fit.pdf}
    \caption{The slope of the free energy for Loschmidt echo (a) and bipartite fidelity (b) in the process $\text{DN}+\text{DN}\rightarrow\lambda+\text{DN}$. The total system size is $N=35k$ sites with the same parameters in Fig.~\ref{fig:DDDD}. The numerical value of exponents follow a quadratic relation as predicted. There is still visible deviation from the analytic results in (a) due to the subtle zero mode, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.12\pi $ and $0.24\pi$. The finite size effect do not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
      \label{fig:DDNN}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=1\columnwidth]{PP_fit.pdf}
    \includegraphics[width=1\columnwidth]{PP_fidel_fit.pdf}
    \caption{The decay exponent of Loschmidt echo (a) and bipartite fidelity (b) $\text{P}+\text{P}\rightarrow\lambda+\text{P}$. The parameters are the same as those in Fig.~\ref{fig:DDNN}. The plot is symmetric with respect to $\theta=0.25\pi$ as predicted. The deviation around $\frac{\pi}{4}$ in (a) is small but visible, see the discussion in the main text. Inset in (a): From the top to bottom, we show the power law decay of Loschmidt echo with $\theta=0.02\pi, 0.08\pi $ and $0.18\pi$. The finite size effect do not emerge before $t=10^{4}$. We use the same curve fitting method as described for Fig.~\ref{fig:DDDD}.}
    \label{fig:PPPP}
    \todo[inline]{Mao: Put the PP for echo;}
\end{figure}
